Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2017-11-26 paper.tex
updating Acknowledgements

This work has been supported in part by projects PreTEL (PRM
Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752
(Spanish Ministry of Economy and Competitiveness and FEDER), and
PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada,
Spain).
% Is still this last grant running?

>>>>

This work has been partially funded by projects 
PreTEL (PRM Consultores - Trevenque S.L.)
EphemeCH TIN2014-56494-C4-3-P, 
DeepBio TIN2017-85727-C4-2-P    and 
TEC2015-68752 
(Spanish Ministry of Economy and Competitiveness and FEDER).
